Storing messages with multipartite neural cliques

### 2014-06-25 Articles/article.tex
...

@@

	For multiple iterations $a$-winner take all is an improvement.

	"$a$-Winners take all" better than "winner takes all" with errors instead of erasures.

	For errors : only better than only 1 activity per cluster if multiple iterations of the $a$-winners take all rule.
	For one iteration, it is less efficient.

	\subsection{Simulations}
		Improves the retrieval rate for multiple iterations and/or corrupted messages.
	\begin{figure}
		\includegraphics[width=8.5cm]{densiteexemple.pdf}
		\caption{Theoretical and empirical densities}
	\end{figure}

>>>>

	\subsection{Simulations}
		Improves the retrieval rate for multiple iterations and/or corrupted messages.

@@

	For multiple iterations $a$-winners take all is a significant improvement.

		"$a$-winners take all" better than "winner takes all" with errors instead of erasures, even for one iteration.

	For errors : only better than only 1 activity per cluster if multiple iterations of the $a$-winners take all rule.
	For one iteration, it is less efficient.
	\begin{figure}
		\includegraphics[width=8.5cm]{densiteexemple.pdf}
		\caption{Theoretical and empirical densities}
	\end{figure}
